\bf $\mathsf{TEDAT}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-19 paper.tex
more on Bandwidth Availability

\begin{document}
\title{\bf $\mathsf{TEDAT}$: Boosting Bandwidth-based Availability Over Inter-DC WAN}

@@

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{TEDAT}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth-based availability} provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{TEDAT}$ is able to maximize revenue when network fails.
%$\mathsf{TEDAT}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{TEDAT}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{TEDAT}$ over inter-DC WAN.
The three core components of  $\mathsf{TEDAT}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using real testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{TEDAT}$ can speed up the online admission control by 30 $\times$ at the expense of 5\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{TEDAT}$ can meet the availability SLAs for 40\% more bandwidth demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{TEDAT}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{TEDAT}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Such negative impacts on inter-DC WAN services will ultimately translate into monetary loss (e.g., refund to customers).
At the same time, as more business moves to cloud, 

@@

\textit{Second}, existing techniques mainly focus on the availability of network reachability, but ignore that users not only have diverse demands on bandwidth,  but also ask for different levels of reliability. Providing reliable bandwidth can be a value-added service for many cloud providers, typically in the form of 

@@

For example, Microsoft Azure guarantees its customers at least 99.9\% availability for backup service and 99.95\% availability for ExpressRoute service \cite{azure}.

@@

\textit{One-size-fit-all} approaches (e.g., TEAVAR \cite{Teavar})  ignoring these heterogeneities cannot support such SLAs well, and may even hurt critical and uninterruptible applications when there are competitions on bandwidth. 

@@

such heterogeneities and competitions are also not considered by current failure recovery approaches, especially those who allocate bandwidth aggressively \cite{Teavar,swan}, since they may run into congestions when rerouting traffic under network failures. 
Such violations of SLAs will inevitably cause revenue loss, which should be reduced as much as possible.

@@

Firstly, we advocate traffic engineering with \textit{bandwidth-based availability} (BA) provision: 
a BA demand $(d, \beta, \alpha, \gamma)$ means that it requests bandwidth $d$ for a life duration between $\alpha$ and $\gamma$, and should be guaranteed at least $\beta\%$ of the duration, subjected to the network capacity and possible failures. Such a demand is typically represented by a Service Level Agreement (see Table \ref{target} for real world examples), and different users or applications may pose different demands. 
%a tenant's \textit{promised bandwidth of service $j$ should be available at least $\beta_j\%$ time}.  
%It tries to guarantee the bandwidth demands from tenants under network uncertainty.
We show that state-of-the-art traffic engineering schemes fail to meet the heterogeneous bandwidth-based availability demands, especially under diverse link failure probabilities that may vary by several orders of magnitude (see $\S$\ref{background}).
%meet services' bandwidth-based availability targets under arbitrarily link failures (see $\S$\ref{background}).
%This is due to the fact that these schemes either ignore the difference in link failure probabilities that can vary by several orders of magnitude in practice or fail to consider the diverse availability targets of services.
%The stronger availability can impel network to provide stable services.
%Compared with the connectivity-based availability, it makes a further step and tries to guarantee the minimal bandwidth demands under network uncertainty after the success of connections.
%
%Taking the diverse availability demands from different applications and the application importance into consideration,

@@

a novel traffic engineering  framework that aims for bandwidth based availability provision over inter-DC WAN (see $\S$\ref{HATE}).

@@

The admission control strikes a good balance between efficiency and optimality, so that new demands can be admitted and guaranteed as much as possible with negligible delay.

@@

To cope with the complexity which increases exponentially with network size,  we further propose a pruning method by ignoring certain failure scenarios that hardly happen.

@@

Thirdly, 
we implement $\mathsf{TEDAT}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as real trace driven simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{TEDAT}$ with state-of-the-art TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{TEDAT}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of 5\% higher rejection ratio;
(2) meet the availability SLAs for 40\% more bandwidth demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{TEDAT}$ is the first to tackle bandwidth based availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under TEDAT, links can maintain high utilization.

@@

\textbf{Availability directly translates into profit.}
Nowadays, high availability is nearly always one of the main items in SLAs  \cite{amazon,azure,amazon2}, and customers are eligible for a credit refund  if there are SLA violations. 
We conduct a survey on the SLA claims of different cloud providers, and Table \ref{target} shows their declared availability targets and  corresponding refunding policies,
%when violated.
%We can see that service providers often use a progressive piecewise function to derive refunding credits for violating availability targets. 
where the refunding credit is typically represented by a simple step function. 
For example, Microsoft Azure provides 10\% refund if its Traffic Manager service availability falls between 99.99\% and
99.0\%, and provides 30\% refund for anything below 99.0\% availability \cite{azure};
Offering high service availability under network failures to retain a good profit is a big challenge.

@@

\textbf{A one-size-fit-all network availability target is not enough.}
%Availability has attracted major attention both in the industry and research community.
%Firstly, most of them only consider \textit{connectivity-based} availability\cite{hong2018b4}, which is conservative.
%The connectivity-based availability\cite{hong2018b4} is defined as the service uptime percentage, where a given minute is considered up if the connection is reachable and  it tries to quickly detour failed network devices, but \textit{they only focus on the reachability of networks and do not provide performance guarantees}.
%as a result, user experience might be influenced.
%Bandwidth on InterDC-WAN is a valuable resource and Microsoft \cite{swan} even spends millions of dollars on WAN investment.
In recent years, there has been a rapid increase in deploying realtime services (video streaming, online game, instant messaging, live broadcast, etc.) over clouds.
Many studies have shown that users will quickly abandon sessions if the qualify of service is not guaranteed, leading to significant losses in revenue for content providers \cite{video1,video2,video3}.
Multiple services might be simultaneously launched over the global infrastructure operated by the same content provider or cloud provider. 
They might also pose different availability requirements, and  will contend for the  
% multiple service instances over different data centers globally at any time.
inter-DC WAN bandwidth.
% is a valuable resource and can become bottleneck \cite{swan} when  services \textit{contend} for network resource.
%In reality, availability targets vary with services, 
As shown in  Table \ref{target}, the minimal availability demands of the Data Transmission Service \cite{alibaba2} and the Short Message Service\cite{alibaba3} are 95\% and 90\%, respectively.
\textit{Such heterogeneous availability demands cannot be well captured and handled by a one-size-fit-all approach}, where all users get the same level of availability guarantee (e.g, TEAVAR  \cite{Teavar} only considers guaranteeing all users' bandwidth at least  $\beta\%$  time) . 
%Therefore, TEAVAR's guarantee such as "Users' bandwidth should be guaranteed at least $\beta\%$ time " \cite{Teavar}  is not enough,
%since it fails to differentiate availability targets of services.

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\subsubsection{Testbed setup}
We build a small testbed with 6 servers to emulate an inter-DC WAN with 6 DCs as in Figure \ref{testbed}.
Each server equips with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, and runs Centos 7 64-bit version with Linux 4.15.6 kernel \cite{Kermel}.
Each inter-DC WAN link is emulated using 1Gbps physical link.
We use 4-shortest path to decide tunnel set of each node pair.
Controller locates in DC1 and runs the software defined networking framework.
We add 100ms delay to emulate the WAN environment.
We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Each VM belongs to only one customer and will send  \textit{iperf} UDP flows with specified rates to other DCs.
We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio.
%Each VM has a demand and the it varies with a period of 3-minutes pattern just as \cite{swan}.  
%The importance of services are randomly chosen from \{1,2,3,4,5\} 
%All services have the same level of importance and availability targets of services are from the SLAs of Azure \cite{azure}.
The network agent in broker runs Floodlight \cite{floodlight} as the OpenFlow controller.
In each data center, all hosts and  NICs connect to an Open vSwitch \cite{openvswitch}.
We start an extra VM in DC1 as the controller. 
%CPU, memory and disk are not the bottleneck in our experiments.
All switches run link liveness detection protocol, and they report any failures to brokers.
Every second, we randomly generate an integer $p$ between 0 and 10000 for each link.
If  $p/10000$ is smaller than the failure probability shown in Figure \ref{testbed}, we disable the network interface to emulate link failure.
Then after 3 seconds, we enable the network interface to emulate link repair.
We also evaluate FFC \cite{FFC} and TEAVAR \cite{Teavar} to make comparisons.
%We mainly care about the following metrics:
%(1) Availability.  Bandwidth-based availability is measured as the time qualification ratio. A second is regarded as qualified if the gap between total measured bandwidth and bandwidth demand is less than 1\%;
%(2) Data loss ratio. We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio;
%(3) Demand rejection ration of different admission control algorithms;
%(4) Profit loss after link failures.
%The achieved  availability is computed as the fraction of qualified seconds, where . 
%We perform the experiment for a duration of 100 minutes.
%We deploy 5 applications and each instance will send traffic to other VMs located in the rest DCs.
%The importance of applications are randomly chosen from \{1,2,3,4,5\} with poisson distribution.
% Availability target of applications are randomly chosen from \{90\%, 95\%, 99\%, 99.9\%, 99.99\%\} with uniform distribution.

@@

\subsubsection{A public cloud example}
We firstly evaluate with a public cloud case.
Assume tenants arrive with poisson process with arrival rate 2 every minute and the duration of each bandwidth demand is under exponential distribution with a mean of 5 minute.
Tenant' bandwidth demands between each node pair are under uniform distribution between 10Mbps and 50Mbps.
The profit of each tenant (i.e., $w_i$) is proportional to his/her total bandwidth demand.
Tenants' availability targets and refunding ratio are from the SLAs of Azure \cite{azure}.
We perform each experiment 100 minutes and repeat the process 20 times, where the error bars paints the maximal, minimal and mean value.

Figure \ref{e2}(a) demonstrates $\mathsf{TEDAT}$ only performs slightly worse than the optimal solution (about 4\%) and is at least 2 $\times$ better than the \textit{Fixed} admission control.
This is because $\mathsf{TEDAT}$ fully considers the availability diversity of tenants.
In contrast, \textit{Fixed} admission control can't change tenants' routing during runtime and such inflexibility leads to higher rejection rate. 
Figure \ref{e2}(b) shows once a tenant's demand is admitted, $\mathsf{TEDAT}$ can guarantee bandwidth.
FFC and TEAVAR with \textit{Fixed} admission control perform slightly better than when they are without admission control since many tenants' demands are rejected, but they also perform worse than $\mathsf{TEDAT}$, because FFC is too conservative and and TEAVAR ignores the diverse demands.
Figure \ref{e2}(c) shows $\mathsf{TEDAT}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.
This is because $\mathsf{TEDAT}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.
Figure \ref{e2}(d) demonstrates data loss ratio after network fails, where $\mathsf{TEDAT}$ performs about 8\% worse than FFC.
FFC performs best since it keeps network utilization low and almost no congestion occurs when network fails, 
while $\mathsf{TEDAT}$ focuses on Monetary gain rather than data loss.
%, where  FFC-1 and FFC-2 
%denote FFC with and without Fixed admission control,  respectively.
%where TEAVAR-1 and TEAVAR-2 are 
%denote TEAVAR with and without Fixed admission control, 
%We can see that 
%Specially, more than 85\% services achieve  95\% availability under $\mathsf{TEDAT}$, while only about 73\% and 60\%  services achieve this target under TEAVAR and FFC.
%Figure \ref{e2}(c) illustrates three schemes have similar performance for services with small availability target (i.e., $<95\%$).
%However, for services with large availability targets (i.e., $>=99\%)$,  $\mathsf{TEDAT}$ performs up to  20\% and 30\% better than TEAVAR and FFC.
%The reason for this is that $\mathsf{TEDAT}$ considers the diverse availability demands, so services with large targets can plunder
%bandwidth from others.
%Compared with TEAVAR, 20\% more applications satisfy their bandwidth demand with $\mathsf{TEDAT}$.
%Figure  \ref{e2}(c) shows the scheduled results with the same parameters.
%We can see the results approximate to that shown in Figure \ref{e2}(b).
%The gap is narrow, about 5\% on average.
%In the following evaluation, we develop a simulator to perform trace-driven simulations.
%Figure \ref{e2}(d) demonstrates the availability deviation between the testbed and simulation under the same parameters.
%We can see that the error is narrow, i.e., more than 90\% time the difference is less than 5\%.

>>>>

\begin{document}
\title{\bf $\mathsf{TEDAT}$: Boosting Bandwidth Availability Over Inter-DC WAN}

@@

\begin{abstract}
Inter-DataCenter Wide Area Network (Inter-DC WAN) that connects geographically distributed data centers is becoming one of the most critical network infrastructures.
%Network failures are common in WANs, so the provision of high availability has been a major focus of network research.
Due to the limited bandwidth resources and inevitable link failures, it is highly challenging to guarantee network availability for services, especially those with stringent bandwidth demands, over inter-DC WAN.
%While modern datacenter services increasingly call for high availability, network failures in WANs remain a fairly common phenomenon.
%Most traffic engineering schemes only consider connectivity-based availability and this severely degrades quality of service, thus revenue.
We present $\mathsf{TEDAT}$,
a novel Traffic Engineering (TE)  framework that 
%contains admission control, online scheduling and failure recovery.
aims for \textit{bandwidth availability} provision, where a service level agreement (SLA) defines that a demand on certain bandwidth should be satisfied with a stipulated probability,  when subjected to the network capacity and possible failures of the inter-DC WAN.
%Also, $\mathsf{TEDAT}$ is able to maximize revenue when network fails.
%$\mathsf{TEDAT}$ tries to guarantee the bandwidth-based availability of demands . 
%$\mathsf{TEDAT}$ generates a probabilistic failure model from empirical data and maximizes the profit that can be achieved under certain constrains on  bandwidth-based availability. 
%For the failure model, we propose a pruning algorithm to reduce the problem size.
%For the optimization problem, we prove it is NP-hard and  propose a greedy algorithm to efficiently solve it with only minor profit loss. 
%We design and implement an SDN-based system named $\mathsf{Dionysus}$ to deploy $\mathsf{TEDAT}$ over inter-DC WAN.
The three core components of  $\mathsf{TEDAT}$, i.e., admission control, traffic scheduling and failure recovery, are built on different mathematical models and theoretically analyzed. 
They are also extensively compared against state-of-the-art TE schemes, using testbed as well as trace driven simulations across different topologies, traffic matrices and failure scenarios. 
Our evaluation demonstrates that, compared with the optimal admission strategy, $\mathsf{TEDAT}$ can speed up the online admission control by 30 $\times$ at the expense of a 5\% higher rejection ratio. 
On the other hand, compared with the latest TE schemes like FFC and TEAVAR,   $\mathsf{TEDAT}$ can meet the bandwidth availability SLAs for 40\% more demands, and when network failure causes SLA violations, it can retain 25\% more profit  under a simple pricing and refunding model.
%.
% $\mathsf{TEDAT}$ can 
%(1) achieve 30 $\times$ speedup in admission control time at the expense of sacrificing 8\% in performance compared to the optimal stragety;
%(2) increase the percentage of demands that satisfy their availability SLAs by up to 40\%;
%(3) hold 30\% more profit for the provider when network fails. 
%The evaluation results demonstrate that $\mathsf{TEDAT}$ can make 20\%, 25\%, 30\%, 40\% more flows satisfy their bandwidth-based availability demands  than TEAVAR, SMORE, SWAN and FFC, respectively.
\end{abstract}

@@

Such negative impacts on inter-DC WAN services will ultimately translate into monetary loss (e.g., more refund to customers in the short term, and low customer stickness in the long term).
At the same time, as more businesses move to cloud, 

@@

\textit{Second}, existing techniques mainly focus on the availability of the whole network, but ignore that users not only have diverse demands on bandwidth,  but also ask for different levels of reliability. Providing reliable bandwidth can be a value-added service for many cloud providers, typically in the form of 

@@

For example, Microsoft Azure guarantees its customers at least 99.9\% availability for its backup service and 99.95\% availability for its ExpressRoute service \cite{azure}.

@@

A \textit{one-size-fit-all} approach (e.g., TEAVAR \cite{Teavar})  ignoring these heterogeneities cannot support such SLAs well, and may even hurt critical and uninterruptible applications when there are competitions on bandwidth. 

@@

such heterogeneities and competitions are also not considered by current failure recovery approaches, especially those who allocate bandwidth aggressively \cite{Teavar,swan}, since they may run into congestions when traffic is rerouted under network failures. 
Such violations of SLAs will inevitably cause revenue loss, which should be kept as small as possible.

@@

Firstly, we advocate traffic engineering with \textit{bandwidth availability} (\textit{BA}) provision: 
a \textit{BA} demand $(d, \beta, \alpha, \gamma)$ means that it requests bandwidth $d$ for a life duration between $\alpha$ and $\gamma$, and should be guaranteed at least $\beta\%$ of the duration, subjected to the network capacity and possible failures. Such a demand is typically represented by a Service Level Agreement (see Table \ref{target} for real world examples), and different users or applications may pose different demands. 
%a tenant's \textit{promised bandwidth of service $j$ should be available at least $\beta_j\%$ time}.  
%It tries to guarantee the bandwidth demands from tenants under network uncertainty.
We show that state-of-the-art traffic engineering schemes fail to meet the heterogeneous bandwidth  availability demands, especially under diverse link failure probabilities that may vary by several orders of magnitude (see $\S$\ref{background}). We note that, although the general concept of bandwidth-based availability has been considered in some TE works \cite{Google BwE, B4-after}, their methodologies and evaluations are actually targeting only a soft guarantee, i.e., the ratio of the allocated bandwidth to the negotiated one, while we will provide a hard guarantee, i.e., the negotiated bandwidth must be met.

%meet services' bandwidth-based availability targets under arbitrarily link failures (see $\S$\ref{background}).
%This is due to the fact that these schemes either ignore the difference in link failure probabilities that can vary by several orders of magnitude in practice or fail to consider the diverse availability targets of services.
%The stronger availability can impel network to provide stable services.
%Compared with the connectivity-based availability, it makes a further step and tries to guarantee the minimal bandwidth demands under network uncertainty after the success of connections.
%
%Taking the diverse availability demands from different applications and the application importance into consideration,

@@

a novel traffic engineering  framework that aims for bandwidth availability provision over inter-DC WAN (see $\S$\ref{HATE}).

@@

The admission control step strikes a balance between efficiency and optimality, so that new demands can be admitted and guaranteed as much as possible with negligible delay.

@@

To cope with the complexity which increases exponentially with the network size,  we also propose a pruning method by ignoring certain failure scenarios that hardly happen.

@@

Thirdly, 
we implement $\mathsf{TEDAT}$ as a real system, including a centralized controller and multiple brokers (one for each DC),  together with end-host clients (see $\S$\ref{system}).
 We conduct extensive experiments using a small testbed as well as trace driven large scale simulations (see $\S$\ref{evaluation}).
We compare  $\mathsf{TEDAT}$ with state-of-the-art WAN TE schemes such as TEAVAR \cite{Teavar}, SMORE \cite{SMORE}, SWAN \cite{swan}, B4 \cite{B4} and FFC \cite{FFC}, across different topologies, traffic matrices and failure scenarios.
Our evaluation demonstrates that $\mathsf{TEDAT}$ can 
(1) speed up the online admission control by 30 $\times $ at the expense of a rejection ratio that is 5\% higher than the optimal strategy;
(2) meet the bandwidth availability SLAs for 40\% more demands;
(3) retain 25\% more profit when network failure causes SLA violations, under a simple pricing and refunding model. 
To our knowledge, $\mathsf{TEDAT}$ is the first to tackle bandwidth availability provision over inter-DC WAN, where heterogeneities of demands and link failures are systematically taken into account for profit maximization.  
 %At last, we show the related works (see $\S$\ref{relate}).
%Traditionally, links are heavily underutilized to achieve a more rigorous availability target. 
%However, in reality, the failure probability of a single link can even differ by three orders of magnitude.
%Therefore, some link failure can be negligible and it makes no sense to reduce the utilization of these links.
%With the link Under TEDAT, links can maintain high utilization.

@@

\textbf{High availability directly translates into profit.}
Nowadays, high availability is nearly always one of the main items in SLAs  \cite{amazon,azure,amazon2}, and customers are eligible for a credit refund  if there are SLA violations. 
We conduct a survey on the SLA claims of different cloud providers, and Table \ref{target} shows their declared availability targets and  corresponding refunding policies,
%when violated.
%We can see that service providers often use a progressive piecewise function to derive refunding credits for violating availability targets. 
where the refunding credit is typically represented by a simple step function. 
For example, Microsoft Azure provides 10\% refund if its Traffic Manager service availability falls between 99.99\% and
99.0\%, and provides 30\% refund for anything below 99.0\% availability \cite{azure}. As more realtime and mission-critical applications (financial trading, online game, video streaming,
instant messaging, live broadcast, etc.) are deployed on the Internet, providing hard guarantee of high service availability under network failures to retain a good profit is a big challenge.

@@

\textbf{A one-size-fit-all network availability target is not enough.}
%Availability has attracted major attention both in the industry and research community.
%Firstly, most of them only consider \textit{connectivity-based} availability\cite{hong2018b4}, which is conservative.
%The connectivity-based availability\cite{hong2018b4} is defined as the service uptime percentage, where a given minute is considered up if the connection is reachable and  it tries to quickly detour failed network devices, but \textit{they only focus on the reachability of networks and do not provide performance guarantees}.
%as a result, user experience might be influenced.
%Bandwidth on InterDC-WAN is a valuable resource and Microsoft \cite{swan} even spends millions of dollars on WAN investment.
In recent years, there has been a rapid increase in rapid and agile deployment of services over clouds.
Many studies have shown that users will quickly abandon sessions if the qualify of service is not guaranteed, leading to significant losses in revenue for content providers \cite{video1,video2,video3}.
Multiple services might be simultaneously launched over the global infrastructure operated by the same content provider or cloud provider. 
They might also pose different availability requirements, and  will contend for the  
% multiple service instances over different data centers globally at any time.
inter-DC WAN bandwidth.
% is a valuable resource and can become bottleneck \cite{swan} when  services \textit{contend} for network resource.
%In reality, availability targets vary with services, 
As shown in  Table \ref{target}, the minimal availability demands of the Data Transmission Service \cite{alibaba2} and the Short Message Service\cite{alibaba3} are 95\% and 90\%, respectively.
\textit{Such heterogeneous availability demands cannot be well captured and handled by a one-size-fit-all approach}, where all users get the same level of availability guarantee (e.g, TEAVAR  \cite{Teavar} only considers guaranteeing all users' bandwidth at least  $\beta\%$  time) . 
%Therefore, TEAVAR's guarantee such as "Users' bandwidth should be guaranteed at least $\beta\%$ time " \cite{Teavar}  is not enough,
%since it fails to differentiate availability targets of services.

@@

\subsection{Testbed evaluation}\label{testbed-evaluation}
\subsubsection{Testbed setup}
We build a small testbed with 6 servers to emulate an inter-DC WAN with 6 DCs as in Figure \ref{testbed}.
Each server equips with 4 Intel Xeon E5-2620 CPUs, 64GB memory and 4 Ethernet NICs, and runs Centos 7 64-bit version with Linux 4.15.6 kernel \cite{Kermel}.
Each inter-DC WAN link is emulated using 1Gbps physical link.
We use 4-shortest path to decide tunnel set of each node pair.
Controller locates in DC1 and runs the software defined networking framework.
We add 100ms delay to emulate the WAN environment.
We start 21 VMs (1 vCPU, 2GB memory, 100GB disk) in each server, where 20 VMs are used to emulate the hosts and 1 VM runs as the broker.
Each VM belongs to only one customer and will send  \textit{iperf} UDP flows with specified rates to other DCs.
%Each VM has a demand and the it varies with a period of 3-minutes pattern just as \cite{swan}.  
%The importance of services are randomly chosen from \{1,2,3,4,5\} 
%All services have the same level of importance and availability targets of services are from the SLAs of Azure \cite{azure}.
The network agent in broker runs Floodlight \cite{floodlight} as the OpenFlow controller.
In each data center, all hosts and  NICs connect to an Open vSwitch \cite{openvswitch}.
We start an extra VM in DC1 as the controller. 
%CPU, memory and disk are not the bottleneck in our experiments.
All switches run link liveness detection protocol, and they report any failures to brokers.
Every second, we randomly generate an integer $p$ between 0 and 10000 for each link.
If  $p/10000$ is smaller than the failure threshold shown in Figure \ref{testbed}, we disable the network interface to emulate link failure.
Then after 3 seconds, we enable the network interface to emulate link repair.
We also evaluate FFC \cite{FFC} and TEAVAR \cite{Teavar} to make comparisons.
%We mainly care about the following metrics:
%(1) Availability.  Bandwidth-based availability is measured as the time qualification ratio. A second is regarded as qualified if the gap between total measured bandwidth and bandwidth demand is less than 1\%;
%(2) Data loss ratio. We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio;
%(3) Demand rejection ration of different admission control algorithms;
%(4) Profit loss after link failures.
%The achieved  availability is computed as the fraction of qualified seconds, where . 
%We perform the experiment for a duration of 100 minutes.
%We deploy 5 applications and each instance will send traffic to other VMs located in the rest DCs.
%The importance of applications are randomly chosen from \{1,2,3,4,5\} with poisson distribution.
% Availability target of applications are randomly chosen from \{90\%, 95\%, 99\%, 99.9\%, 99.99\%\} with uniform distribution.

@@

\subsubsection{A public cloud example}
We firstly evaluate a public cloud case.
Assume tenants arrive at the public cloud under poisson process with mean arrival rate 2 every minute and the duration of each bandwidth demand is under exponential distribution with a mean of 5 minutes.
Bandwidth demands between each node pair are under uniform distribution between 10Mbps and 50Mbps.
Every 1Mbps is sold 1$\$$.
%The profit of each tenant (i.e., $w_i$) is proportional to his/her total bandwidth demand.
Availability targets and refunding ratio are randomly chosen from Azure SLAs \cite{azure}.
Each experiment lasts 100 minutes and is repeated 20 times, where the error bars paints the maximal, minimal and mean value.

Figure \ref{e2}(a) demonstrates $\mathsf{TEDAT}$ only performs slightly worse than the optimal solution (about 4\%) and is at least 2 $\times$ better than the \textit{Fixed} admission control.
This is because $\mathsf{TEDAT}$ fully considers the availability diversity of tenants.
In contrast, \textit{Fixed} admission control can't change tenants' routing during runtime and such inflexibility leads to higher rejection rate. 
Figure \ref{e2}(b) shows once a tenant's demand is admitted, $\mathsf{TEDAT}$ can guarantee bandwidth.
FFC and TEAVAR with \textit{Fixed} admission control perform slightly better than when they are without admission control since many tenants' demands are rejected, but they also perform worse than $\mathsf{TEDAT}$, because FFC is too conservative and and TEAVAR ignores the diverse demands.
Figure \ref{e2}(c) shows $\mathsf{TEDAT}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.
This is because $\mathsf{TEDAT}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.
We measure total bytes loss according to \textit{iperf} server side reports and packet counters in the switches, then finally derive the data loss ratio.
Figure \ref{e2}(d) demonstrates data loss ratio after network fails, where $\mathsf{TEDAT}$ performs about 8\% worse than FFC.
FFC performs best since it keeps network utilization low and almost no congestion occurs when network fails, 
while $\mathsf{TEDAT}$ focuses on Monetary gain rather than data loss.
%, where  FFC-1 and FFC-2 
%denote FFC with and without Fixed admission control,  respectively.
%where TEAVAR-1 and TEAVAR-2 are 
%denote TEAVAR with and without Fixed admission control, 
%We can see that 
%Specially, more than 85\% services achieve  95\% availability under $\mathsf{TEDAT}$, while only about 73\% and 60\%  services achieve this target under TEAVAR and FFC.
%Figure \ref{e2}(c) illustrates three schemes have similar performance for services with small availability target (i.e., $<95\%$).
%However, for services with large availability targets (i.e., $>=99\%)$,  $\mathsf{TEDAT}$ performs up to  20\% and 30\% better than TEAVAR and FFC.
%The reason for this is that $\mathsf{TEDAT}$ considers the diverse availability demands, so services with large targets can plunder
%bandwidth from others.
%Compared with TEAVAR, 20\% more applications satisfy their bandwidth demand with $\mathsf{TEDAT}$.
%Figure  \ref{e2}(c) shows the scheduled results with the same parameters.
%We can see the results approximate to that shown in Figure \ref{e2}(b).
%The gap is narrow, about 5\% on average.
%In the following evaluation, we develop a simulator to perform trace-driven simulations.
%Figure \ref{e2}(d) demonstrates the availability deviation between the testbed and simulation under the same parameters.
%We can see that the error is narrow, i.e., more than 90\% time the difference is less than 5\%.
